---
title: "Tensor_splines_cos_function_target_2_covariates"
author: "Sai Pradeep Peri"
date: "10/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
```


```{r, eval=TRUE}
### define the fine spatial grids for each GP, the spatial resolution
### will be between -2 and 2 for all dimensions for simplicity
num_fine_int <- 100

fine_grid_list <- list(
  x1 = seq(-2, 2, length.out = num_fine_int+1),
  x2 = seq(-2, 2, length.out = num_fine_int+1)
)
fine_grid_list
```



```{r, eval=TRUE}
### set the true relationships per factor

### set the functional expressions

true_functions <- list(
  g1 = function(x, av){av$a0 + av$a1 * cos(av$a2 * pi * x)},
  g2 = function(x, av){av$a0 + av$a1 * cos(av$a2 * pi * x)}
)

### set the parameters of the functions
true_hypers <- list(
  g1 = list(a0 = 0, a1 = 1, a2 = 1),
  g2 = list(a0 = 0, a1 = 1, a2 = 1)
)
```


```{r, eval=TRUE}
### define a wrapper function for executing the functions
run_factors <- function(myfunc, myx, myparams)
{
  myfunc(myx, myparams)
}
```


```{r, eval=TRUE}
### calculate each of the factors over the fine grid
fine_true_factors <- purrr::pmap(list(true_functions,
                                      fine_grid_list,
                                      true_hypers),
                                 run_factors)

fine_true_factors
```

```{r, eval=TRUE}
fine_true_latent_dfs <- purrr::pmap(list(fine_grid_list,
                                         fine_true_factors,
                                         1:2),
                                    function(x, g, glabel){tibble::tibble(x = x, g = g) %>% 
                                        purrr::set_names(c(sprintf("x%d", glabel),
                                                           sprintf("g%d", glabel))) %>% 
                                        tibble::rowid_to_column(sprintf("x%d_id", glabel))})

fine_true_latent_dfs
```



```{r, eval=TRUE}
### create the tensor product of the two factors
fine_latent_tensor <- expand.grid(fine_grid_list,
            KEEP.OUT.ATTRS = FALSE,
            stringsAsFactors = FALSE) %>% 
  as.data.frame() %>% tbl_df() %>% 
  left_join(fine_true_latent_dfs[[1]], by = "x1") %>% 
  left_join(fine_true_latent_dfs[[2]], by = "x2") %>% 
  select(ends_with("_id"), x1:x2, g1, g2) %>% 
  tibble::rowid_to_column("fine_id")
fine_latent_tensor
```

```{r, eval=TRUE}
### visualize the sum of the first two factors
fine_latent_tensor %>% 
  count(x1, x2, g1, g2) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = g1 + g2)) +
  coord_equal() +
  scale_fill_viridis_c() +
  theme_bw()
```

# ```{r, eval=TRUE}
# fine_latent_tensor %>%
#   mutate(Additive = g1 + g2, Multiplicative = g1 * g2, Interaction = g1 + g2 + g1 * g2)
# ```


## Additve part only

```{r}
library(splines)
Xfine_add <- model.matrix( ~ ns(x1, 4) + ns(x2, 5), data = fine_latent_tensor)
Xfine_add %>% colnames()
```



```{r}
Xfine_add %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  select(-`(Intercept)`) %>% 
  tibble::rowid_to_column() %>% 
  left_join(fine_latent_tensor %>% tibble::rowid_to_column(),
            by = "rowid") %>% 
  tidyr::gather(key = "key", value = "value", -rowid, -x1, -x2) %>% 
  tidyr::separate(key,
                  c("left_word", "right_word"),
                  sep = ":",
                  fill = "right",
                  remove = FALSE) %>% 
  filter(is.na(right_word)) %>% 
  tidyr::separate(left_word,
                  c("ns_word", "feature_word"),
                  sep = ",",
                  remove = FALSE) %>% 
  tidyr::separate(feature_word,
                  c("dof", "s_id"),
                  sep = "\\)") %>% 
  mutate(dof = stringr::str_trim(dof, side = "both")) %>% 
  filter(!is.na(dof)) %>%
  tidyr::separate(ns_word,
                  c("ns_ltr", "variable"),
                  sep = "\\(",
                  remove = FALSE) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = value,
                            group = interaction(variable, dof, s_id))) +
  facet_grid(s_id ~ variable + dof, labeller = "label_both") +
  scale_fill_viridis_b() +
  theme_bw()
```

### generate the coefficients to use
```{r}
set.seed(34212)
beta_true <- c(0, rnorm(n = ncol(Xfine_add)-1, mean = 0, sd = 3))
beta_true
```

### calculate the true mean trend on the fine grid
```{r}
mu_true_fine <- as.vector(Xfine_add %*% matrix(beta_true))
```

### visualize the true mean trend
```{r}
fine_latent_tensor %>% 
  mutate(mu = mu_true_fine) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = mu)) +
  scale_fill_viridis_c() +
  theme_bw()
```

```{r}
fine_latent_tensor %>% 
  mutate(mu = mu_true_fine) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = mu)) +
  geom_contour(mapping = aes(z = mu),
               color = "white") +
  scale_fill_viridis_b() +
  theme_bw()
```


### use a small amount of noise
```{r}
set.seed(23785474)
y_fine <- rnorm(n = length(mu_true_fine), mean = mu_true_fine, sd = 0.25)
```

```{r}
fine_latent_tensor %>% 
  mutate(y = y_fine) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = y)) +
  scale_fill_viridis_c() +
  theme_bw()
```

### downsample to a coarse grid
```{r}
coarse_grid <- expand.grid(x1 = seq(-2, 2, length.out = 51),
                           x2 = seq(-2, 2, length.out = 51),
                           KEEP.OUT.ATTRS = FALSE, stringsAsFactors = FALSE) %>% 
  as.data.frame() %>% tibble::as_tibble()
coarse_grid
```


### create the coarse grid training set
```{r}
train_df <- fine_latent_tensor %>% 
  mutate(y = y_fine) %>% 
  inner_join(coarse_grid, by = c("x1", "x2"))
train_df
```


### visualize the training set
```{r}
train_df %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = y)) +
  scale_fill_viridis_c() +
  theme_bw()
```

```{r}
### take a look at the marginal features in the coarse grid
model.matrix( ~ ns(cos(x1), 8) + ns(cos(x2), 7), train_df) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  select(-`(Intercept)`) %>% 
  tibble::rowid_to_column() %>% 
  left_join(coarse_grid %>% tibble::rowid_to_column(),
            by = "rowid") %>% 
  tidyr::gather(key = "key", value = "value", -rowid, -x1, -x2) %>% 
  tidyr::separate(key,
                  c("left_word", "right_word"),
                  sep = ":",
                  fill = "right",
                  remove = FALSE) %>% 
  filter(is.na(right_word)) %>% 
  tidyr::separate(left_word,
                  c("ns_word", "feature_word"),
                  sep = ",",
                  remove = FALSE) %>% 
  tidyr::separate(feature_word,
                  c("dof", "s_id"),
                  sep = "\\)") %>% 
  mutate(dof = stringr::str_trim(dof, side = "both")) %>% 
  filter(!is.na(dof)) %>%
  tidyr::separate(ns_word,
                  c("ns_ltr", "variable"),
                  sep = "\\(",
                  remove = FALSE) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = value,
                            group = interaction(variable, dof, s_id))) +
  facet_grid(s_id ~ variable + dof, labeller = "label_both") +
  scale_fill_viridis_b() +
  theme_bw()
```


```{r}
library(broom)
```


#Function for fitting the model
```{r}
model_fit_func <- function(df_1, df_2,df_3, df_4, data){
  model <- lm(y ~ ns(x1, df = df_1)+ns(x2, df=df_2)+ns(x1, df = df_3):ns(x2, df=df_4), data = data)
  metrics <- glance(model) %>% mutate(df_1 = df_1, df_2 = df_2, df_3 = df_3, df_4 = df_4)
  return(metrics)
}
```


```{r}
degree_of_freedom_grid <- expand.grid(x1 = 4:8, x2 = 4:8, x3 = 0:4, x4 = 0:4, KEEP.OUT.ATTRS = FALSE) %>% as.data.frame() %>% tbl_df()
degree_of_freedom_grid
```

```{r}
library(purrr)
```

```{r}
df_list <- list(degree_of_freedom_grid$x1,degree_of_freedom_grid$x2,degree_of_freedom_grid$x3,degree_of_freedom_grid$x4)
model_comp_df <- pmap_dfr(df_list, model_fit_func, data = train_df)
```


```{r}
model_comp_df[order(model_comp_df$AIC),] %>% select(df_1, df_2, df_3, df_4, AIC)
```



```{r, eval=TRUE}
df_best_AIC_model <- model_comp_df %>% filter(AIC == min(AIC)) %>% select(df_1, df_2, df_3, df_4)
df_best_AIC_model$df_1[1]
```


```{r, eval=TRUE}
best_AIC_fit <- lm(y ~ ns(x1, df = df_best_AIC_model$df_1[1]) + ns(x2, df=df_best_AIC_model$df_2[1]) + ns(x1, df = df_best_AIC_model$df_3[1]):ns(x2, df=df_best_AIC_model$df_4[1]), data = train_df)
best_AIC_fit %>% summary()
coefplot::coefplot(best_AIC_fit) + theme_bw()
```

```{r}
pred_model_fine_grid_ci <- predict(best_AIC_fit, fine_latent_tensor, interval = "confidence")
pred_model_fine_grid_pi <- predict(best_AIC_fit, fine_latent_tensor, interval = "prediction")
```

```{r}
pred_model_fine_grid_df <- pred_model_fine_grid_ci %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  purrr::set_names(c("fit", "ci_lwr", "ci_upr")) %>% 
  bind_cols(pred_model_fine_grid_pi %>% 
              as.data.frame() %>% tibble::as_tibble() %>% 
              purrr::set_names(c("fit", "pred_lwr", "pred_upr")) %>% 
              select(pred_lwr, pred_upr))

pred_model_fine_grid_df %>% summary()
```


### visualize the prediction on the grid
```{r}
fine_latent_tensor %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = fit)) +
  coord_equal() +
  scale_fill_viridis_b() +
  theme_bw()
```

### confidence interval difference
```{r}
fine_latent_tensor %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = ci_upr - ci_lwr)) +
  coord_equal() +
  scale_fill_viridis_b(option = "inferno") +
  theme_bw()
```

### prediction interval difference
```{r}
fine_latent_tensor %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = pred_upr - pred_lwr)) +
  coord_equal() +
  scale_fill_viridis_b(option = "plasma") +
  theme_bw()
```


### look at the error relative to the NOISY fine grid
```{r}
fine_latent_tensor %>% 
  mutate(y = y_fine) %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = abs(y_fine - fit))) +
  coord_equal() +
  scale_fill_viridis_b(option = "magma") +
  theme_bw()
```


### show the coarse grid points for refernece
```{r}
fine_latent_tensor %>% 
  mutate(y = y_fine) %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = abs(y_fine - fit))) +
  geom_point(data = coarse_grid,
             mapping = aes(x = x1, y = x2),
             color = "grey", shape = 0, size = 1) +
  coord_equal() +
  scale_fill_viridis_b(option = "magma") +
  theme_bw()
```


### look at the error relative to the TRUTH
```{r}
fine_latent_tensor %>% 
  mutate(mu = mu_true_fine) %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = abs(mu - fit))) +
  geom_point(data = coarse_grid,
             mapping = aes(x = x1, y = x2),
             color = "grey", shape = 0, size = 1) +
  coord_equal() +
  scale_fill_viridis_b(option = "magma") +
  theme_bw()
```

### look at the error realtive to the TRUTH vs x1
```{r}
fine_latent_tensor %>% 
  mutate(mu = mu_true_fine) %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = abs(mu - fit))) +
  geom_line(mapping = aes(group = x2)) +
  facet_wrap(~x2, labeller = "label_both", nrow = 11) +
  theme_bw()
```

### compare the error relative to the TRUE range
```{r}
fine_latent_tensor %>% 
  mutate(mu = mu_true_fine) %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = abs(mu - fit) / (diff(range(mu_true_fine))))) +
  geom_line(mapping = aes(group = x2)) +
  facet_wrap(~x2, labeller = "label_both", nrow = 11) +
  theme_bw()
```





## Interaction with marginal effects included

```{r, eval=TRUE}
### visualize the sum of the first two factors
fine_latent_tensor %>% 
  count(x1, x2, g1, g2) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = g1 + g2 + g1*g2)) +
  coord_equal() +
  scale_fill_viridis_c() +
  theme_bw()
```

```{r}
library(splines)
Xfine_interact <- model.matrix( ~ ns(g1, 4) + ns(g2, 5) + ns(g1,3):ns(g2,2), data = fine_latent_tensor)
Xfine_interact %>% colnames()
```

### visualize the marginal (main effects) over the grid
```{r}
Xfine_interact %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  select(-`(Intercept)`) %>% 
  tibble::rowid_to_column() %>% 
  left_join(fine_latent_tensor %>% tibble::rowid_to_column(),
            by = "rowid") %>% 
  tidyr::gather(key = "key", value = "value", -rowid, -x1, -x2) %>% 
  tidyr::separate(key,
                  c("left_word", "right_word"),
                  sep = ":",
                  fill = "right",
                  remove = FALSE) %>% 
  filter(is.na(right_word)) %>% 
  tidyr::separate(left_word,
                  c("ns_word", "feature_word"),
                  sep = ",",
                  remove = FALSE) %>% 
  tidyr::separate(feature_word,
                  c("dof", "s_id"),
                  sep = "\\)") %>% 
  mutate(dof = stringr::str_trim(dof, side = "both")) %>% 
  filter(!is.na(dof)) %>%
  tidyr::separate(ns_word,
                  c("ns_ltr", "variable"),
                  sep = "\\(",
                  remove = FALSE) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = value,
                            group = interaction(variable, dof, s_id))) +
  facet_grid(s_id ~ variable + dof, labeller = "label_both") +
  scale_fill_viridis_b() +
  theme_bw()
```

### look at the interaction effects
```{r}
Xfine_interact %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  select(-`(Intercept)`) %>% 
  tibble::rowid_to_column() %>% 
  left_join(fine_latent_tensor %>% tibble::rowid_to_column(),
            by = "rowid") %>% 
  tidyr::gather(key = "key", value = "value", -rowid, -x1, -x2) %>% 
  tidyr::separate(key,
                  c("left_word", "right_word"),
                  sep = ":",
                  fill = "right",
                  remove = FALSE) %>% 
  filter(!is.na(right_word)) %>% 
  tidyr::separate(left_word,
                  c("ns_x1_word", "x1_s_id"),
                  sep = "\\)",
                  remove = FALSE) %>% 
  tidyr::separate(right_word,
                  c("ns_x2_word", "x2_s_id"),
                  sep = "\\)",
                  remove = FALSE) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = value)) +
  facet_grid(x2_s_id ~ x1_s_id, labeller = "label_both") +
  scale_fill_viridis_b() +
  theme_bw()
```

```{r}
set.seed(898123)
beta_true_interact <- c(0, rnorm(n = ncol(Xfine_interact)-1, mean = 0, sd = 3))

beta_true_interact
```


### calculate the true mean trend 

```{r}
mu_true_fine_interact <- as.vector(Xfine_interact %*% matrix(beta_true_interact))
```

### visualize the true mean trend
```{r}
fine_latent_tensor %>% 
  mutate(mu = mu_true_fine_interact) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = mu)) +
  scale_fill_viridis_c() +
  theme_bw()
```

```{r}
fine_latent_tensor %>% 
  mutate(mu = mu_true_fine_interact) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = mu)) +
  geom_contour(mapping = aes(z = mu),
               color = "white") +
  scale_fill_viridis_b() +
  theme_bw()
```

### use a small amount of noise
```{r}
set.seed(65656)
y_fine_interact <- rnorm(n = length(mu_true_fine_interact), mean = mu_true_fine_interact, sd = 0.3)
```

```{r}
fine_latent_tensor %>% 
  mutate(y = y_fine_interact) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = y)) +
  scale_fill_viridis_c() +
  theme_bw()
```

### downsample to a coarse grid
```{r}
coarse_grid_interact <- expand.grid(x1 = seq(-2, 2, length.out = 51),
                           x2 = seq(-2, 2, length.out = 51),
                           KEEP.OUT.ATTRS = FALSE, stringsAsFactors = FALSE) %>% 
  as.data.frame() %>% tibble::as_tibble()
coarse_grid_interact
```


### create the training set
```{r}
train_df_interact <- fine_latent_tensor %>% 
  mutate(y = y_fine_interact) %>% 
  inner_join(coarse_grid_interact, by = c("x1", "x2"))
train_df_interact
```

### visualize the training set
```{r}
train_df_interact %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = y)) +
  scale_fill_viridis_c() +
  theme_bw()
```

```{r}
### take a look at the marginal features in the coarse grid
model.matrix( ~ ns(g1, 4) + ns(g2, 5) + ns(g1,3):ns(g2,2), train_df_interact) %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  select(-`(Intercept)`) %>% 
  tibble::rowid_to_column() %>% 
  left_join(coarse_grid %>% tibble::rowid_to_column(),
            by = "rowid") %>% 
  tidyr::gather(key = "key", value = "value", -rowid, -x1, -x2) %>% 
  tidyr::separate(key,
                  c("left_word", "right_word"),
                  sep = ":",
                  fill = "right",
                  remove = FALSE) %>% 
  filter(is.na(right_word)) %>% 
  tidyr::separate(left_word,
                  c("ns_word", "feature_word"),
                  sep = ",",
                  remove = FALSE) %>% 
  tidyr::separate(feature_word,
                  c("dof", "s_id"),
                  sep = "\\)") %>% 
  mutate(dof = stringr::str_trim(dof, side = "both")) %>% 
  filter(!is.na(dof)) %>%
  tidyr::separate(ns_word,
                  c("ns_ltr", "variable"),
                  sep = "\\(",
                  remove = FALSE) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = value,
                            group = interaction(variable, dof, s_id))) +
  facet_grid(s_id ~ variable + dof, labeller = "label_both") +
  scale_fill_viridis_b() +
  theme_bw()
```


```{r}
### interaction effects on the coarse grid
model.matrix( ~ ns(g1, 4) + ns(g2, 5) + ns(g1,3):ns(g2,2), train_df_interact)  %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  select(-`(Intercept)`) %>% 
  tibble::rowid_to_column() %>% 
  left_join(coarse_grid %>% tibble::rowid_to_column(),
            by = "rowid") %>% 
  tidyr::gather(key = "key", value = "value", -rowid, -x1, -x2) %>% 
  tidyr::separate(key,
                  c("left_word", "right_word"),
                  sep = ":",
                  fill = "right",
                  remove = FALSE) %>% 
  filter(!is.na(right_word)) %>% 
  tidyr::separate(left_word,
                  c("ns_x1_word", "x1_s_id"),
                  sep = "\\)",
                  remove = FALSE) %>% 
  tidyr::separate(right_word,
                  c("ns_x2_word", "x2_s_id"),
                  sep = "\\)",
                  remove = FALSE) %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = value)) +
  facet_grid(x2_s_id ~ x1_s_id, labeller = "label_both") +
  scale_fill_viridis_b() +
  theme_bw()
```

#Function for fitting the model
```{r}
model_fit_func_interact <- function(df_1, df_2,df_3, df_4, data){
  model <- lm(y ~ ns(x1, df = df_1)+ns(x2, df=df_2)+ns(x1, df = df_3):ns(x2, df=df_4), data = data)
  metrics <- glance(model) %>% mutate(df_1 = df_1, df_2 = df_2, df_3 = df_3, df_4 = df_4)
  return(metrics)
}
```


```{r}
df_grid_interact <- expand.grid(x1 = 8:12, x2 = 8:12, x3 = 8:12, x4 = 8:12, KEEP.OUT.ATTRS = FALSE) %>% as.data.frame() %>% tbl_df()
df_grid_interact
```

```{r}
df_list_interact <- list(df_grid_interact$x1, df_grid_interact$x2, df_grid_interact$x3, df_grid_interact$x4)
model_comp_df_interact <- pmap_dfr(df_list_interact, model_fit_func_interact, data = train_df_interact)
```

```{r}
model_comp_df_interact[order(model_comp_df_interact$AIC),] %>% select(df_1, df_2, df_3, df_4, AIC)
```

```{r, eval=TRUE}
df_best_AIC_model_interact <- model_comp_df_interact %>% filter(AIC == min(AIC)) %>% select(df_1, df_2, df_3, df_4)
df_best_AIC_model_interact$df_1[1]
```

```{r, eval=TRUE}
best_AIC_fit_interact <- lm(y ~ ns(x1, df = df_best_AIC_model_interact$df_1[1]) + ns(x2, df=df_best_AIC_model_interact$df_2[1]) + ns(x1, df = df_best_AIC_model_interact$df_3[1]):ns(x2, df=df_best_AIC_model_interact$df_4[1]), data = train_df_interact)
best_AIC_fit_interact %>% summary()
coefplot::coefplot(best_AIC_fit_interact) + theme_bw()
```


```{r}
pred_model_interact_fine_grid_ci <- predict(best_AIC_fit_interact, fine_latent_tensor, interval = "confidence")
pred_model_interact_fine_grid_pi <- predict(best_AIC_fit_interact, fine_latent_tensor, interval = "prediction")
```

```{r}
pred_model_interact_fine_grid_df <- pred_model_interact_fine_grid_ci %>% 
  as.data.frame() %>% tibble::as_tibble() %>% 
  purrr::set_names(c("fit", "ci_lwr", "ci_upr")) %>% 
  bind_cols(pred_model_interact_fine_grid_pi %>% 
              as.data.frame() %>% tibble::as_tibble() %>% 
              purrr::set_names(c("fit", "pred_lwr", "pred_upr")) %>% 
              select(pred_lwr, pred_upr))

pred_model_interact_fine_grid_df %>% summary()
```


### visualize the prediction on the grid
```{r}
fine_latent_tensor %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_interact_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = fit)) +
  coord_equal() +
  scale_fill_viridis_b() +
  theme_bw()
```

### confidence interval difference
```{r}
fine_latent_tensor %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_interact_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = ci_upr - ci_lwr)) +
  coord_equal() +
  scale_fill_viridis_b(option = "inferno") +
  theme_bw()
```

### prediction interval difference
```{r}
fine_latent_tensor %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_interact_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = pred_upr - pred_lwr)) +
  coord_equal() +
  scale_fill_viridis_b(option = "plasma") +
  theme_bw()
```

### look at the error relative to the NOISY fine grid
```{r}
fine_latent_tensor %>% 
  mutate(y = y_fine_interact) %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_interact_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = abs(y - fit))) +
  coord_equal() +
  scale_fill_viridis_b(option = "magma") +
  theme_bw()
```


### show the coarse grid points for refernece
```{r}
fine_latent_tensor %>% 
  mutate(y = y_fine_interact) %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_interact_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = abs(y - fit))) +
  geom_point(data = coarse_grid,
             mapping = aes(x = x1, y = x2),
             color = "grey", shape = 0, size = 1) +
  coord_equal() +
  scale_fill_viridis_b(option = "magma") +
  theme_bw()
```

### look at the error relative to the TRUTH
```{r}
fine_latent_tensor %>% 
  mutate(mu = mu_true_fine_interact) %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_interact_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = x2)) +
  geom_raster(mapping = aes(fill = abs(mu - fit))) +
  geom_point(data = coarse_grid,
             mapping = aes(x = x1, y = x2),
             color = "grey", shape = 0, size = 1) +
  coord_equal() +
  scale_fill_viridis_b(option = "magma") +
  theme_bw()
```


### look at the error realtive to the TRUTH vs x1
```{r}
fine_latent_tensor %>% 
  mutate(mu = mu_true_fine_interact) %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_interact_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = abs(mu - fit))) +
  geom_line(mapping = aes(group = x2)) +
  facet_wrap(~x2, labeller = "label_both", nrow = 11) +
  theme_bw()
```

### compare the error relative to the TRUE range
```{r}
fine_latent_tensor %>% 
  mutate(mu = mu_true_fine_interact) %>% 
  tibble::rowid_to_column() %>% 
  left_join(pred_model_interact_fine_grid_df %>% 
              tibble::rowid_to_column(),
            by = "rowid") %>% 
  ggplot(mapping = aes(x = x1, y = abs(mu - fit) / (diff(range(mu))))) +
  geom_line(mapping = aes(group = x2)) +
  facet_wrap(~x2, labeller = "label_both", nrow = 11) +
  theme_bw()
```


```{r}
```

```{r}
```







